Title

### 2023-10-19 main.tex
.

{\color{green} As before, from the definition of a 1PR, we know that $U(p)$ can be decomposed as $ARB$, where 
$A,B$ are unitary operators acting on the $N$-qubit system
and $R$ is a rotation applied to one qubit.
From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$
rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
Given  this, to prove the result of this theorem,
we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
then $R_{\sigma_3}(2s(p))$ and finally $A$, with
the goal of getting to \eref{eq:uj}. }

>>>>

{\color{green} As before, from the definition of a 1PR, we know that $U(p)$ can be decomposed as $ARB$, where 
$A,B$ are unitary operators acting on the $N$-qubit system
and $R$ is a rotation applied to one qubit.
From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$
rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
To prove this theorem,
we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
then $R_{\sigma_3}(2s(p))$ and finally $A$, with
the goal of getting to \eref{eq:uj}. }
